\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-25 demystify.tex
formatting, minor

\begin{commentbox}[Vu]
One of the reasons I create this document is that my colleagues at GMU are interested in recruiting Vietnamese students and are surprised when seeing very few applications in Vietnam (e.g., each year our CS program receives more than 350 PhD applications, most of which are international but only 3--4 are from Vietnam). In general the number of CS PhD applications from Vietnam to US universities is low and more would be very welcomed. 
\end{commentbox}

@@

\begin{commentbox}[Hakan]
At GMU, for full consideration, students should make sure to submit \textbf{ALL} required documents by the application deadline, and should never assume that some required documents (such as official TOEFL scores or official diplomas/transcripts) will be waived by the admissions office. If something is listed and not marked as ``optional'', it is mandatory and they should plan for submitting all those.  
\end{commentbox}
\paragraph{Why we do not waive application fee?}  This is typically a requirement of the university. Individual departments and programs do not have the flexibility to waive the application fee, even if they want to.

@@

\begin{commentbox}[Vu]
Many international students mention Scopus Q1, which consists of various journals from IEEE, Elsevier, and many other publishers.  I don't know/recognize many of journals listed in Scopus Q1. This might be something to be mindful of, as \textbf{CS} faculty might not be too familiar with Scopus or journals listed there, so devote sometime in your statement to discuss the significance of your papers.
\end{commentbox}

\begin{commentbox}[Craig]
GMU and many other universities allow you to upload your published papers and other writing samples. In many cases, even if the papers were not published at top places, we can still determine their quality by simply skimming over the paper.  
\end{commentbox}

@@

\begin{commentbox}[Hung]
The reputation of VinAI has been increasing steadily over the past few years; many of my colleagues heard about VinAI.
\end{commentbox}

@@

\begin{commentbox}[Thanh]
Due to academic culture, professors in Vietnam usually aim for (international) journals instead of conferences. Could you give some tips on how to know whether a journal is good (CSrankings, unfortunately, only consider conferences)?.
\tcblower
Vu: One way is looking at what well-known researchers publish at. For example, if you are interested in a field X, you can use CSRankings to look at active faculty in X, and then look at their websites to see what journals they publish at.
\end{commentbox}

@@

\begin{commentbox}[Vu]
Some letter writers ask the applicants to write their own letters for them to sign. As mentioned, this will hurt the applicants (admission committee members are actually quite good at determining this)! Multiple students mentioned that  some professor did this so that the applicants do not go abroad or only go to places where they want the students to go to.
\tcblower
Sometimes students would go through great length just to get letters from well-known professors in their school, but the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnam might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about your research ability. It's better to have a good personalized
letter about your own research ability from someone who is less
well-known than a generic/weak letter from a well-known person.
\end{commentbox}

\begin{commentbox}[Hung]
A sad reality is that most professors in Vietnam \textbf{DO NOT} know how to write a good letter, or are lazy in writing letters hence delegate the writing to the students. Unfortunately, there is no easy solution to this problem.
\end{commentbox}

@@

\begin{commentbox}[Hung]
I think asking for a “research vision” from a Ph.D. applicant is too much. Even people graduated with a Ph.D. have a great difficulty in explicating their researh vision. In my opinion, you should focus on showing (not telling) your research passion (if you do have).
\end{commentbox}

@@

\begin{commentbox}[Vu]
I often read the research statement (and the LORs) first. If I am
persuaded by then, I would skim over other factors and advocate for
admission (unless I see red flags in other parts). If I am not
convinced, then I will likely recommend rejection (unless I see
something standout in other parts).
\tcblower
Do careful research on professors, don't mention \emph{emeritus} or  adjunct faculty. 
Also, be careful not to send statements to wrong schools or mixing
facts (e.g., talking about school X but mentioned about working with
profs. at school Y; and definitely do not talk about George Washington when applying to George Mason). I have seen such statements more time that I
should.
\end{commentbox}

@@

\begin{commentbox}[Hung]
I personally don’t care about which schools students attended. There are many other ways to evaluate an applicant.
\end{commentbox}

\begin{commentbox}[Vu]
Sometime PhD admission committee in the US will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. In some cases we ask other faculty and students if we think they know about the place.  For example, when I was a postdoc at UMD, people in admission committee ask me to evaluate applicants from Vietnam.  During my time at UNL and now here at GMU, I have looked at Vietnamese applications (whether they are assigned to me or not) and provide input to their reviewers, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

\begin{commentbox}[Thanh]
Vietnamese universities typically offer specialized programs, such as the talented engineer program at HUST, that have highly competitive entrance exams and a limited number of available slots (e.g., 30 per year). However, these programs often set higher requirements for students, including more demanding tests and assignments, resulting in lower GPAs and overall rankings. For example, an 3.5 GPA students from such talented programs are typically much better than a 4.0 GPA students not in those programs.  Similarly, variations in GPA standards exist among different universities, with technical universities generally having lower GPAs than economical universities. These make gaining admission in the US difficult as US faculty are not familiar with these issues.
\tcblower
\textbf{Vu}: Vietnamese students and even faculty often lament how this competitive/low-grading system hurts Vietnamese students when applying abroad. One way to mitigate this is making these issues known to admission committee in your statement.  Universities with Vietnamese profs are probably aware of them, but in general your letter writers \emph{and} you can explicitly mention these in their letters and your statement.
\end{commentbox}

\paragraph{GRE} Most CS programs in the US \textbf{no longer require GREs}, so you don't need to take them. However, they might be useful for international students from programs we are not familiar with.

\begin{commentbox}[Vu]
Personally I do not pay attention to GRE scores as I do not believe they are good indicator for research. However, if you have good GRE scores then you should include them in your application.
\end{commentbox}

@@

\begin{commentbox}[Vu]
The minimum for GMU (being above this might not mean much, but below is a \red{red flag}).
\begin{itemize}
\item GPA: $\ge 3.0$ in your undergrad (but we also consider the rank/prestige of your school)
\item GRE: not required, though it can help boost your profile
%    \item but if you want to use it, then we expect a total (V+Q) of $\ge 311$ (with a $\ge 157$ Q) and A $\ge 3.0-3.5$.
\item English requirement tests (one of the below)
  \begin{itemize}    
  \item TOEF: 88 pts in total AND $\ge 20$ points in each subsection OR
  \item IELTS: $\ge 6.5$ OR
  \item DuoLingo Graduate English: $\ge 120$ OR 
  \item Pearson Test of Academic English: $\ge 67$
  \end{itemize}  
\end{itemize}
\end{commentbox}

@@

\begin{commentbox}[Vu]
At GMU, we are encouraged to interview candidates. For very strong candidates, the interview is actually to recruit them.  In some cases a faculty interviews a candidate that they see potentials and want to advocate for their admission. Without the interview, such applications may be more likely to be rejected. Overall, being selected for interview means a very good chance of being admitted.
\end{commentbox}

@@

\begin{commentbox}[Vu]
GMU has \emph{Virtual} Open House (VOH), e.g., \url{https://cs-gmu.github.io/cs-phd-voh-s23/}, which I've co-organized in the last two years. We invite all admitted PhD students to the VOH through Zoom to learn about the CS program, the department, GMU, and the DC area in general. Students also get opportunities to chat with professors and current students.
\end{commentbox}

@@

\begin{commentbox}[Vu]
TA and RA at GMU have similar benefits in tuition waiving and insurance.  The college and department will set the rate for 9-month graduate assistant stipend.  TA, which is paid by the department, will likely be that amount but RA might be higher depending on the stage of the student (1st year vs ABD\footnote{All but dissertation: really close to graduate.}) and the prof. 
\tcblower
Having health insurance is required at many US universities.  Do not assume that you're young and healthy and ignore insurance.  At GMU, and at most good CS PhD programs, your GTA or GRA \emph{will always} come with full insurance. In fact, at GMU your spouse/children will get significant discount rate for health insurance.  So you will never have to worry much about health issues for you or your family here.
\end{commentbox}

@@

\paragraph{How to get TA?}  Unless you have other funding such as RA or Fellowships, TA is typically a default thing. When you apply to be a full-time student,  state that you need financial assistant. It is common that the PhD committee will either admit you and give you GTA, or reject you; i.e., we do not admit a student without supporting them.

\begin{commentbox}[Vu]
At GMU CS, students admitted with TA have  4 years of GTA guaranteed and also receive  stipend for the \textbf{first} summer.
\end{commentbox}

Even if you have other funding and do not need TA, you still should do TA at least once.  This allows you to see what teaching is like, which is especially helpful for research career where you often give talks and tell people about your work. Note that GMU sometimes has classes that a more senior student can teach.  In that case, you will be paid as a lecturer, which is higher than GTA.  This is a good opportunity for students to get teaching experience and also get paid more.
\subsection{Research Assistant (RA)}
RA is provided through a professor through their own funding so you can work on their project.  
You do not need to teach as an RA, so you can focus on your research. Depending on the professor, RA may be available during the summer. \S\ref{sec:ra-cost} gives more details on RA budget.

@@

\begin{commentbox}[Vu]
If you got recruited by a prof. who would give you RA right away, it's very likely you will get admitted.  For example, if a prof., even if not in PhD admission committee, wants to work with and funds you, the PhD admission committee will respect that decision and admit you (unless your application has many red flags).
\end{commentbox}

@@

\begin{commentbox}[Vu]
At GMU, PhD applicants are automatically eligible for a Presidential Fellowship.  It is at least as good as GTA but the most important thing is that as a fellowship it is truly free money (i.e., you are not depending on any prof. or TA duties).  PhD admission committee members nominate applicants for this fellowship and the committee will vote and give the fellowship to the top 2.
\end{commentbox}

@@

International students not familiar with US universities often put them into \emph{two} bins:  (i) very top schools that they dream about such as Stanford, MIT, Princeton, Harvard and (ii) everything else.  In many cases, they use resources such as rankings from US News, which are \emph{highly} questionable\footnote{\url{https://cra.org/cra-statement-us-news-world-report-rankings-computer-science-universities/}}.  Sometimes these students evaluate CS programs using the reputations non-CS programs such as medical, math, or physics.
They even rank universities based on popular states they know in the US, e.g., California and New York.  Clearly, there are so many thing wrong with these methods.

@@

\begin{commentbox}[Hung]
I always encourage the students I admitted to talk with my students and the students of other faculty in other schools who admitted them. You will unlikely hear straight-out complaints from current students in a professor’s group. But sometimes what is important are things that they (current students) don’t tell you. Pay attention to their "level of excitement" being in the group.
\end{commentbox}

@@

The short answer is that tenured-track faculty such as assistant professors are more likely to be young and active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. However, they may not have as much experience in managing students and may not have as much funding (yet).

@@

\begin{commentbox}[Thanh]
    In my opinion, having a well-suited advisor is crucial for a successful PhD and research career. One effective approach to finding a suitable professor is by working with a professor during your undergraduate studies. An exemplary instance is VinAI's residency program, where residents collaborate with professors from the US for two years before applying to PhD programs. Many VinAI residents have achieved remarkable results and gained admission to prestigious US universities. Unfortunately, VinAI's resident program is limited to AI research.

@@

% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

% \begin{commentbox}[Thanh]
% \end{commentbox}

@@

\paragraph{Referring to professors you know} Here, because you are already familiar with these individuals, you can just informally use their firstname (or Dr./Prof., if you want to be formal) as mentioned above. You can also include their institution if it makes it more precise.  For example, I did my postdoc with Jeff Foster at Univ. of Maryland.   Do not include ranking (e.g., Assistant, Associate, Scientist, ...) when referring to someone. I see many international students include a lengthy title of people they know, e.g., my advisor is Asst. Prof. X, and I also collaborate with ACM Distinguished Scientist Y.  This is \emph{not necessary} and makes it look like you're trying to show off your connections. In short, these nuances represent some cultural differences that you may encounter and will gradually adapt to. More on cultural differences in \S\ref{sec:cultural}.

>>>>

\begin{commentbox}[Vu:]
One of the reasons I create this document is that my colleagues at GMU are interested in recruiting Vietnamese students and are surprised when seeing very few applications in Vietnam (e.g., each year our CS program receives more than 350 PhD applications, most of which are international but only 3--4 are from Vietnam). In general the number of CS PhD applications from Vietnam to US universities is low and more would be welcomed. 
\end{commentbox}

@@

\begin{commentbox}[Hakan:]
At GMU, for full consideration, students should make sure to submit \textbf{ALL} required documents by the application deadline, and should never assume that some required documents (such as official TOEFL scores or official diplomas/transcripts) will be waived by the admissions office. If something is listed and not marked as ``optional'', it is mandatory and they should plan for submitting all those.  
\end{commentbox}
\paragraph{Why we do not waive application fee?}  This is typically a requirement of the university. Individual departments and programs do not have the flexibility to waive the application fee, even if they want to.

@@

\begin{commentbox}[Vu:]
Many international students mention Scopus Q1, which consists of various journals from IEEE, Elsevier, and many other publishers.  I don't know/recognize many of journals listed in Scopus Q1. This might be something to be mindful of, as \textbf{CS} faculty might not be too familiar with Scopus or journals listed there, so devote sometime in your statement to discuss the significance of your papers.
\end{commentbox}

\begin{commentbox}[Craig:]
GMU and many other universities allow you to upload your published papers and other writing samples. In many cases, even if the papers were not published at top places, we can still determine their quality by simply skimming over the paper.  
\end{commentbox}

@@

\begin{commentbox}[Hung:]
The reputation of VinAI has been increasing steadily over the past few years; many of my colleagues heard about VinAI.
\end{commentbox}

@@

\begin{commentbox}[Thanh:]
Due to academic culture, professors in Vietnam usually aim for (international) journals instead of conferences. Could you give some tips on how to know whether a journal is good (CSrankings, unfortunately, only consider conferences)?.
\tcblower
Vu: One way is looking at what well-known researchers publish at. For example, if you are interested in a field X, you can use CSRankings to look at active faculty in X, and then look at their websites to see what journals they publish at.
\end{commentbox}

@@

\begin{commentbox}[Vu:]
Some letter writers ask the applicants to write their own letters for them to sign. As mentioned, this will hurt the applicants (admission committee members are actually quite good at determining this)! Multiple students mentioned that  some professor did this so that the applicants do not go abroad or only go to places where they want the students to go to.
\tcblower
Sometimes students would go through great length just to get letters from well-known professors in their school, but the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnam might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about your research ability. It's better to have a good personalized
letter about your own research ability from someone who is less
well-known than a generic/weak letter from a well-known person.
\end{commentbox}

\begin{commentbox}[Hung:]
A sad reality is that most professors in Vietnam \textbf{DO NOT} know how to write a good letter, or are lazy in writing letters hence delegate the writing to the students. Unfortunately, there is no easy solution to this problem.
\end{commentbox}

@@

\begin{commentbox}[Hung:]
I think asking for a “research vision” from a Ph.D. applicant is too much. Even people graduated with a Ph.D. have a great difficulty in explicating their researh vision. In my opinion, you should focus on showing (not telling) your research passion (if you do have).
\end{commentbox}

@@

\begin{commentbox}[Vu:]
I often read the research statement (and the LORs) first. If I am
persuaded by then, I would skim over other factors and advocate for
admission (unless I see red flags in other parts). If I am not
convinced, then I will likely recommend rejection (unless I see
something standout in other parts).
\tcblower
Do careful research on professors, don't mention \emph{emeritus} or  adjunct faculty. 
Also, be careful not to send statements to wrong schools or mixing
facts (e.g., talking about school X but mentioned about working with
profs. at school Y; and definitely do not talk about George Washington when applying to George Mason). I have seen such statements more time that I
should.
\end{commentbox}

@@

\begin{commentbox}[Hung:]
I personally don’t care about which schools students attended. There are many other ways to evaluate an applicant.
\end{commentbox}

\begin{commentbox}[Vu:]
Sometime PhD admission committee in the US will share a document such as \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Foreign-Top-Schools}{this one}, which lists the top schools in several countries. In some cases we ask other faculty and students if we think they know about the place.  For example, when I was a postdoc at UMD, people in admission committee ask me to evaluate applicants from Vietnam.  During my time at UNL and now here at GMU, I have looked at Vietnamese applications (whether they are assigned to me or not) and provide input to their reviewers, e.g., X is the top tech school in Vietnam and so it should be \emph{top} instead of \emph{unknown} foreign, which makes a huge difference.
\end{commentbox}

@@

\begin{commentbox}[Thanh:]
Vietnamese universities typically offer specialized programs, such as the talented engineer program at HUST, that have highly competitive entrance exams and a limited number of available slots (e.g., 30 per year). However, these programs often set higher requirements for students, including more demanding tests and assignments, resulting in lower GPAs and overall rankings. For example, an 3.5 GPA students from such talented programs are typically much better than a 4.0 GPA students not in those programs.  Similarly, variations in GPA standards exist among different universities, with technical universities generally having lower GPAs than economical universities. These make gaining admission in the US difficult as US faculty are not familiar with these issues.
\tcblower
\textbf{Vu}: Vietnamese students and even faculty often lament how this competitive/low-grading system hurts Vietnamese students when applying abroad. One way to mitigate this is making these issues known to admission committee in your statement.  Universities with Vietnamese profs are probably aware of them, but in general your letter writers \emph{and} you can explicitly mention these in their letters and your statement.
\end{commentbox}

\paragraph{GRE} Most good CS PhD programs in the US \textbf{no longer require GREs}, so you don't need to take them. However, they might be useful for international students from programs we are not familiar with.

\begin{commentbox}[Vu:]
Personally I do not pay attention to GRE scores as I do not believe they are good indicator for research. However, if you have good GRE scores then you should include them in your application.
\end{commentbox}

@@

\begin{commentbox}[Vu:]
The minimum for GMU (being above this might not mean much, but below is a \red{red flag}).
\begin{itemize}
\item GPA: $\ge 3.0$ in your undergrad (but we also consider the rank/prestige of your school)
\item GRE: not required, though it can help boost your profile
%    \item but if you want to use it, then we expect a total (V+Q) of $\ge 311$ (with a $\ge 157$ Q) and A $\ge 3.0-3.5$.
\item English requirement tests (one of the below)
  \begin{itemize}    
  \item TOEF: 88 pts in total AND $\ge 20$ points in each subsection OR
  \item IELTS: $\ge 6.5$ OR
  \item DuoLingo Graduate English: $\ge 120$ OR 
  \item Pearson Test of Academic English: $\ge 67$
  \end{itemize}  
\end{itemize}
\end{commentbox}

@@

\begin{commentbox}[Vu:]
At GMU, we are encouraged to interview candidates. For very strong candidates, the interview is actually to recruit them.  In some cases a faculty interviews a candidate that they see potentials and want to advocate for their admission. Without the interview, such applications may be more likely to be rejected. Overall, being selected for interview means a very good chance of being admitted.
\end{commentbox}

@@

\begin{commentbox}[Vu:]
GMU has \emph{Virtual} Open House (VOH), e.g., \url{https://cs-gmu.github.io/cs-phd-voh-s23/}, which I've co-organized in the last two years. We invite all admitted PhD students to the VOH through Zoom to learn about the CS program, the department, GMU, and the DC area in general. Students also get opportunities to chat with professors and current students.
\end{commentbox}

@@

\begin{commentbox}[Vu:]
TA and RA at GMU have similar benefits in tuition waiving and insurance.  The college and department will set the rate for 9-month graduate assistant stipend.  TA, which is paid by the department, will likely be that amount but RA might be higher depending on the stage of the student (1st year vs ABD\footnote{All but dissertation: really close to graduate.}) and the prof. 
\tcblower
Having health insurance is required at many US universities.  Do not assume that you're young and healthy and ignore insurance.  At GMU, and at most good CS PhD programs, your GTA or GRA \emph{will always} come with full insurance. In fact, at GMU your spouse/children will get significant discount rate for health insurance.  So you will never have to worry much about health issues for you or your family here.
\end{commentbox}

@@

\paragraph{How to get TA?}  Unless you have other funding such as RA or Fellowships, TA is typically a default thing for good CS PhD programs. When you apply to be a full-time student,  state that you need financial assistant. It is common that the PhD committee will either admit you and give you GTA, or reject you; i.e., we do not admit a student without supporting them.

\begin{commentbox}[Vu:]
At GMU CS, students admitted with TA have  4 years of GTA guaranteed and also receive  stipend for the \textbf{first} summer.
\end{commentbox}

Even if you have other funding and do not need TA, you still should do TA at least once.  This allows you to see what teaching is like, which is especially helpful for research career where you often give talks and tell people about your work. GMU sometimes has classes that a more senior student can teach.  In that case, you will be paid as GTA or even sometimes as a lecturer.  This is a good opportunity for students to get teaching experience and also get paid more (as a lecturer).

\subsection{Research Assistant (RA)}
RA is provided through a professor through their own funding so you can work on their project.  
You do not need to teach as an RA, so you can focus on your research. Depending on the professor, RA may be available during the summer. \S\ref{sec:ra-cost} gives more details on RA budget.

@@

\begin{commentbox}[Vu:]
If you got recruited by a prof. who would give you RA right away, it's very likely you will get admitted.  For example, if a prof., even if not in PhD admission committee, wants to work with and funds you, the PhD admission committee will respect that decision and admit you (unless your application has many red flags).
\end{commentbox}

@@

\begin{commentbox}[Vu:]
At GMU, PhD applicants are automatically eligible for a Presidential Fellowship.  It is at least as good as GTA but the most important thing is that as a fellowship it is truly free money (i.e., you are not depending on any prof. or TA duties).  PhD admission committee members nominate applicants for this fellowship and the committee will vote and give the fellowship to the top 2.
\end{commentbox}

@@

International students not familiar with US universities often put them into \emph{two} bins:  (i) very top schools that they dream about, and (ii) everything else.  In many cases, they use resources such as rankings from US News, which are \emph{highly} questionable\footnote{\url{https://cra.org/cra-statement-us-news-world-report-rankings-computer-science-universities/}}.  Sometimes these students evaluate CS programs using the reputations non-CS programs such as medical, math, or physics.
They even rank universities based on popular states they know in the US, e.g., California and New York.  Clearly, there are so many thing wrong with these methods.

@@

\begin{commentbox}[Hung:]
I always encourage the students I admitted to talk with my students and the students of other faculty in other schools who admitted them. You will unlikely hear straight-out complaints from current students in a professor’s group. But sometimes what is important are things that they (current students) don’t tell you. Pay attention to their "level of excitement" being in the group.
\end{commentbox}

@@

%The tenure system in universities in the US (and other countries) can be confusing. In most cases, you probably don't need to know much about it. But it is helpful to know a few things so you know how to find PhD advisor. First, faculty of a CS (and other) department can be divided into 2 types:  (i) tenured and tenure-track and (ii) non-tenured or teaching faculty.  Tenured/Tenure -track faculty focus on research and related tasks such as mentoring and getting grants to support students, etc. Their teaching load is very light, typically they just teach 1 or at most 2 classes a semester.  Non-tenured/teaching faculty focuses on teaching, and often teach 3-4 classes per semester.  They can mentor Ph.D. students but they typically cannot serve as a formal advisor of Ph.D. students (i.e., they cannot graduate PhD students). Note that there is also affiliated faculty who is tenured/tenure-track profs. from another department. They can serve in Ph.D. dissertation committee but they likely cannot serve as the main advisor of CS students.

The short answer is that tenure-track faculty such as assistant professors are more likely to be young and active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. However, they may not have as much experience in managing students and may not have as much funding (yet).

@@

\begin{commentbox}[Thanh:]
    In my opinion, having a well-suited advisor is crucial for a successful PhD and research career. One effective approach to finding a suitable professor is by working with a professor during your undergraduate studies. An exemplary instance is VinAI's residency program, where residents collaborate with professors from the US for two years before applying to PhD programs. Many VinAI residents have achieved remarkable results and gained admission to prestigious US universities. Unfortunately, VinAI's resident program is limited to AI research.

@@

% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh:]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

% \begin{commentbox}[Thanh:]
% \end{commentbox}

@@

\paragraph{Referring to professors you know} Here, because you are already familiar with these individuals, you can just informally use their firstname (or Dr./Prof., if you want to be formal) as mentioned above. You can also include their institution if it makes it more precise.  For example, I did my postdoc with Jeff Foster at Univ. of Maryland.   Do not include ranking (e.g., Assistant, Associate, Scientist, ...) when referring to someone. I see many international students include a lengthy title of people they know, e.g., my advisor is Asst. Prof. X, and I also collaborate with NASA Distinguished Scientist Y.  This is \emph{not necessary} and makes it look like you're trying to show off your connections. In short, these nuances represent some cultural differences that you may encounter and will gradually adapt to. More on cultural differences in \S\ref{sec:cultural}.
